THE HERA DISH III : MEASURING ELEMENT CHROMATICITY WITH REFLECTOMETRY.

### 2016-09-13 DishReflectometry/Paper1_v3.tex
Edits to abstract

\begin{abstract}
Spectral structure of the systematics has so far been the most dominant
limiting factor for the experiments attempting to detect the redshifted 21~cm
signal from the Epoch of Reionization (EoR). Systematics are specific to
instruments and their direct measurement or estimation is not always
straightforward. The Hydrogen Epoch of Reionization Array (HERA) uses the delay
spectrum technique for estimating of 21~cm power spectrum. In a unique way, the
delay spectrum technique directly translates to reflectometry in case of
measuring instrumental response and allows the direct measurement of systematic
effects in individual array element.  This paper presents a detailed
investigation of the instrument chromaticity of an antenna element that
constitute Hydrogen Epoch of Reionization Array. Reflectometry measurements are
carried out on a HERA dish-feed assembly between 100 to 200~MHz which studies
the multiple reflections in the system that finally results in various spurious
spectral response in the measured visibility. Reflectometry measurements shows
that even without incorporation of any sophisticated analysis method, the
instrument is capable of measuring the line of sight component  of the $k$ mode
$k_{\parallel} >0.2 h Mpc^{-1}$ modes of power spectrum with very low
foreground contaminations around $k_{\parallel} \approx0.2 h Mpc^{-1}$.  The
performance is significantly better at the high frequency subbands of
observation. When combined with a powerful foreground suppression method such
as inverse covariance weighting, the instrument is capable of measuring the
power spectrum for the spatial modes as low as $k_{\parallel} >0.1$. The study
presented here qualifies HERA as a power spectrum instrument and serves as a
fundamental method to design and measure instrument systematics for any future
experiment that aims to detect the 21~cm EoR power spectrum.  
\end{abstract}

>>>>

\begin{abstract}
Spectral structure from instrumental systematics is the current
limiting factor for the experiments attempting to detect the redshifted 21~cm
signal from the Epoch of Reionization (EoR). 
Recent advances in the delay spectrum methodology for measuring the
21~cm EoR power spectrum have brought new attention to the impact that
the frequency performance of antenna elements has on the viability of
making this challenging measurement.
%Systematics are specific to
%instruments and their direct measurement or estimation is not always
%straightforward. 
%The Hydrogen Epoch of Reionization Array (HERA) uses the delay
%spectrum technique for estimating of 21~cm power spectrum. 
In particular, the delay spectrum formalism provides a relationship
between time-domain reflectrometry profiles that can be directly
measured with a vector network analyzer (VNA) and the power spectrum modes accessible
to a 21~cm EoR experiment.
%In a unique way, the
%delay spectrum technique directly translates to reflectometry in case of
%measuring instrumental response and allows the direct measurement of systematic
%effects in individual array element.  
In this paper, we derive the explicit relationship between $S_{11}$ measurements
made by a VNA and the corresponding convolving kernel in delay space.
Using this formalism, we examine
the spectral chromaticity of the prototype antenna elements that
constitute Hydrogen Epoch of Reionization Array (HERA) 
between 100 and 200~MHz.
These reflectometry measurements exhibit spurious chromatic structure relative
to electromagnetic simulations, but we find 
that even without compensating for this structure, the antenna element
will support measuring $k$ modes with line-of-sight components 
$k_{\parallel} >0.2 h~Mpc^{-1}$.  
%The performance is significantly better at the high frequency subbands of observation. 
When combined with the powerful foreground weighting methods used in optimal
quadratic estimation,
HERA should be capable of measuring the
power spectrum at $k_{\parallel} > 0.1$. This study
qualifies HERA as a power spectrum instrument and serves as an
important method for designing and measuring instrumental systematics for any future
experiment aiming to detect the 21~cm EoR power spectrum.  
\end{abstract}
